### 2016-10-11 paper/intro.tex
Renamed paper directory and updated .gitignore file

Optimizing regression testing is important.  As software evolves the
size of test sets increases, potentially leading to disruption in the
development process caused by late reports of test failures.  This
problem manifests more dramatically at large IT companies
(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
Microsoft~\Fix{cite}) where the size of test sets often exceeds the
size of the code base.  Several approaches have been proposed to
optimize regression testing.  Research has focused mostly on test
selection~\Fix{cite}, test reduction~\Fix{cite}, and test
prioritization~\Fix{cite}.  Although these approaches can also be
applied in industrial settings, \Fix{the focus in industry has been
mostly in parallelizing execution of tests using server farms, /Is
this an assumption? Is there any evidence?} where worker machines
from the farm are assigned to execute distinct subsets of the original
test suite.

>>>>

Optimizing regression testing is important.  As software evolves the
size of test sets increases, potentially leading to disruption in the
development process caused by late reports of test failures.  This
problem manifests more dramatically at large IT companies
(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
Microsoft~\Fix{cite}) where the size of test sets often exceeds the
size of the code base.  Several approaches have been proposed to
optimize regression testing.  Research has focused mostly on test
selection~\Fix{cite}, test reduction~\Fix{cite}, and test
prioritization~\Fix{cite}.  Although these approaches can also be
applied in industrial settings, the focus in industry has been
mostly in parallelizing execution of tests using server
farms,\Fix{@Jean: Is
this an assumption? Is there any evidence?} where worker machines
from the farm are assigned to execute distinct subsets of the original
test suite.
